A formal theory of digital twins

### 2023-10-31 manuscripts/xxx-2024/main.tex
continue working on real world model

    \section{A digital twin theory}
    \label{section:theory}
    In the following, we introduce a formal theory of digital twins.
    We start with introducing core concepts in Section~\ref{section:theory-core}.
    Then, on top of the core concepts we build a theory of the real world in Section~\ref{section:theory-world}.
    Finally, on top of the theory of the real world we derive a theory of digital twins in Section~\ref{section:theory-twin}.

    \subsection{Core concepts}
    \label{section:theory-core}

    \begin{figure}[htbp]
        \centering
        \includegraphics{./figures/theory-core.pdf}
        \caption{Illustration of core concepts}
        \label{figure:theory-core}
    \end{figure}

@@

    \subsubsection{Behavior}
    Finally, we include a generic model of how state changes over time.
    Analogous to the previous two cases, concrete models of time and state can be plugged in easily.
    In our approach, a behavior is a mapping from the time domain to the state domain, i.e.
    \[
        \overrightarrow{S}: T \rightarrow S.
    \]

    \subsection{TODO}
    TODO

    \subsubsection{Observer}
    TODO

    \subsubsection{Observation}
    TODO

    \subsubsection{Event}
    TODO time point and time span (observer dependent)

    \subsection{Our model of the real world}
    \label{section:theory-world}

    \begin{figure}[htbp]
        \centering
        \includegraphics{./figures/theory-world.pdf}
        \caption{Illustration of real world concepts}
        \label{figure:theory-world}
    \end{figure}

@@

    \subsubsection{World state}
    TODO
    \[
        S_{World} = (S_{Prod}, S_{Env}).
    \]

    \subsubsection{Product state}
    In our theory, the product state describes the product perfectly at a particular point in time.
    We assume perfect knowledge in this representation and, hence, the representation is only a theoretical construct.
    Mathematically, the product state is defined as set
    \[
        S_{Prod}.
    \]

    \subsubsection{Environment state}
    Similarly, the environment state describes the environment perfectly at a particular point in time.
    Again we assume perfect knowledge in this purely theoretical representation.
    Hence, the environment state is defined mathematically as set
    \[
        S_{Env}.
    \]

    \subsubsection{World behavior}
    TODO
    \[
        \overrightarrow{S_{World}} = (\overrightarrow{S_{Prod}}, \overrightarrow{S_{Env}})
    \]

    \subsection{TODO}
    TODO

    \subsubsection{Input}
    TODO

    \subsubsection{Output}
    TODO

    \subsubsection{Function}
    TODO

    %\subsubsection{Product function}
    %Based on product and environment state we can define the product function.
    %The product function describes the logic of how the product reacts to the environment.
    %This logic can be described as mapping from environment behavior to product behavior, i.e.
    %\[
    %    F_{Prod}: \overrightarrow{S_{Env}} \rightarrow \overrightarrow{S_{Prod}}
    %\]

    %\subsubsection{Environment function}
    %Similarly, we can define the environment function.
    %The environment function describes the logic of how the environment reacts to the product.
    %Hence, this logic can be described as mapping from product behavior to environment behavior, i.e.
    %\[
    %    F_{Env}: \overrightarrow{S_{Prod}} \rightarrow \overrightarrow{S_{Env}}
    %\]

    %\subsubsection{World behavior}
    %Finally, based on product state and function as well as environment state and function we introduce world behavior.
    %In our theory, world behavior is a combination of consistent product and environment behavior.
    %We express world behavior as tuple
    %\[
    %    B_{World} = (\overrightarrow{S_{Prod}}, \overrightarrow{S_{Env}})
    %\]
    %such that the environment behavior $\overrightarrow{S_{Env}}$ is the result of product behavior $\overrightarrow{S_{Prod}}$, i.e.
    %\[
    %    \overrightarrow{S_{Env}} = F_{Env}(\overrightarrow{S_{Prod}})
    %\]
    %and, adversely, the product behavior $\overrightarrow{S_{Prod}}$ is the result of environment behavior $\overrightarrow{S_{Env}}$, i.e.
    %\[
    %    \overrightarrow{S_{Prod}} = F_{Prod}(\overrightarrow{S_{Env}}).
    %\]

>>>>

    \section{A digital twin theory}
    \label{section:theory}
    In the following, we introduce a formal theory of digital twins.
    We start with introducing core concepts in Section~\ref{section:theory-core}.
    Then, on top of the core concepts we build a theory of the real world in Section~\ref{section:theory-universe}.
    Finally, on top of the theory of the real world we derive a theory of digital twins in Section~\ref{section:theory-twin}.

    \subsection{Time, state, and trace}
    \label{section:theory-core}

    \begin{figure}[htbp]
        \centering
        \includegraphics{./figures/theory-core.pdf}
        \caption{Illustration of time, state, and trace.}
        \label{figure:theory-core}
    \end{figure}

@@

    \subsubsection{Trace}
    Finally, we include a generic model of how state changes over time.
    Analogous to the previous two cases, concrete models of time and state can be plugged in easily.
    In our approach, a behavior is a mapping from the time domain to the state domain, i.e.
    \[
        \overrightarrow{S}: T \rightarrow S.
    \]

    \subsection{Product, environment, and universe}
    \label{section:theory-universe}

    \begin{figure}[htbp]
        \centering
        \includegraphics{figures/theory-universe.pdf}
        \caption{Illustration of product, environment, and universe.}
        \label{figure:theory-universe}
    \end{figure}

@@

    \subsubsection{Product}
    In our theory, the product state describes the product perfectly at a particular point in time.
    We assume perfect knowledge in this representation and, hence, the representation is only a theoretical construct.
    Mathematically, the product state is defined as set
    \[
        S_{Prod}.
    \]
    TODO
    \[
        \overrightarrow{S_{Pro}}: T \rightarrow S_{Pro}.
    \]

    \subsubsection{Environment}
    Similarly, the environment state describes the environment perfectly at a particular point in time.
    Again we assume perfect knowledge in this purely theoretical representation.
    Hence, the environment state is defined mathematically as set
    \[
        S_{Env}.
    \]
    TODO
    \[
        \overrightarrow{S_{Env}}: T \rightarrow S_{Env}.
    \]

    \subsubsection{Universe}
    TODO
    \[
        S_{Uni} = S_{Pro} \times S_{Env}.
    \]
    TODO
    \[
        \overrightarrow{S_{Uni}}: T \rightarrow S_{Uni}.
    \]
    TODO
    \[
        \overrightarrow{S_{Uni}}: T \rightarrow S_{Pro} \times S_{Env}.
    \]
    such that $\forall t \in T$
    \[
        \overrightarrow{S_{Uni}}(t) = (\overrightarrow{S_{Pro}}(t), \overrightarrow{S_{Env}}(t))
    \]

    \subsection{Function}
    TODO

    \begin{figure}[htbp]
        \centering
        \includegraphics{./figures/theory-world.pdf}
        \caption{Illustration of real world concepts}
        \label{figure:theory-function}
    \end{figure}

    \subsubsection{Function}
    Based on the concept of product and environment we can define the product function.
    The product function describes the logic of how the product reacts to the environment state over time.
    This logic can be described as mapping from environment trace to product trace, i.e.
    \[
        F_{Pro}: \overrightarrow{S_{Env}} \rightarrow \overrightarrow{S_{Pro}}
    \]
    Similarly, we can define the environment function.
    The environment function describes the logic of how the environment reacts to the product state over time.
    Hence, this logic can be described as mapping from product trace to environment trace, i.e.
    \[
        F_{Env}: \overrightarrow{S_{Pro}} \rightarrow \overrightarrow{S_{Env}}
    \]

    %\subsubsection{Universe function}
    %Finally, based on product state and function as well as environment state and function we introduce world behavior.
    %In our theory, world behavior is a combination of consistent product and environment behavior.
    %We express world behavior as tuple
    %\[
    %    B_{World} = (\overrightarrow{S_{Pro}}, \overrightarrow{S_{Env}})
    %\]
    %such that the environment behavior $\overrightarrow{S_{Env}}$ is the result of product behavior $\overrightarrow{S_{Prod}}$, i.e.
    %\[
    %    \overrightarrow{S_{Env}} = F_{Env}(\overrightarrow{S_{Pro}})
    %\]
    %and, adversely, the product behavior $\overrightarrow{S_{Prod}}$ is the result of environment behavior $\overrightarrow{S_{Env}}$, i.e.
    %\[
    %    \overrightarrow{S_{Prod}} = F_{Pro}(\overrightarrow{S_{Env}}).
    %\]

    %\subsection{TODO}
    %TODO

    %\subsubsection{Observer}
    %TODO

    %\subsubsection{Observation}
    %TODO

    %\subsubsection{Event}
    %TODO time point and time span (observer dependent)
